
# IST 707 DATA ANALYTICS PROJECT- CODE CLEANING

### Uploading Dataset
#### Reading the Training data csv and storing it into a dataframe
```{r}
setwd("C:/Users/bhavi/OneDrive/Desktop/SYR ADS/Sem 2/IST_707_Data_Analytics/Project/DontGetKicked")

getwd

first_read_car_buy_df <- read.csv("training.csv")
```


```{r}
str(first_read_car_buy_df)
summary(first_read_car_buy_df)
```

#### REPLACING string NULL with NAs
```{r}
for (i in 1:length(first_read_car_buy_df)){
  for (j in 1:nrow(first_read_car_buy_df)){
    if(first_read_car_buy_df[j, i] == "NULL"){
      first_read_car_buy_df[j, i] <- NA
    }
  }
}
```


#### Identifying number of NAs in DATAFRAME
```{r}
sum(is.na(first_read_car_buy_df))
```

### 1. THE TRIM COLUMN has 2360 blanks which needs to be imputed
```{r}
length(first_read_car_buy_df$Trim[first_read_car_buy_df$Trim == "" | is.na(first_read_car_buy_df$Trim) | first_read_car_buy_df$Trim == "NULL"])
```

#### REPLACE MISSING VALUES WITH MODE AT MAKE MODEL level
```{r}
## FUNCTION TO OBTAIN MODE of a VECTOR
  getmode <- function(x) {
  ux <- na.omit(unique(x) )
 tab <- tabulate(match(x, ux)); 
 ux[tab == max(tab)]
 ux[1]
}
```


```{r}
#library(tidyverse)
#mode_trim_make_model <- first_read_car_buy_df %>%
#      group_by(Make,Model)%>%
#      summarise(getmode(Trim))
#colnames(mode_trim_make_model) <- c('make','model','mode')
```

```{r}
#indexOfNA <- which(first_read_car_buy_df$Trim == "")
#for (i in indexOfNA) {
#      first_read_car_buy_df$Trim[i] <- mode_trim_make_model[mode_trim_make_model$make == first_read_car_buy_df[i,"make"] & mode_trim_make_model$model == #first_read_car_buy_df[i,"model"],3]
#    }

first_read_car_buy_df$Trim[first_read_car_buy_df$Trim == ""| is.na(first_read_car_buy_df$Trim)] <- getmode(first_read_car_buy_df$Trim)

```

#### 0 blank values after replacing with Mode
```{r}
length(first_read_car_buy_df$Trim[first_read_car_buy_df$Trim == ""|is.na(first_read_car_buy_df$Trim)])
```

### 2. The Submodel column has 8 NULL or Blank values, which can be replaced with the mode of the value
```{r}
length(first_read_car_buy_df$SubModel[first_read_car_buy_df$SubModel == ""|is.na(first_read_car_buy_df$SubModel)])
```

```{r}
first_read_car_buy_df$SubModel[first_read_car_buy_df$SubModel == ""|is.na(first_read_car_buy_df$SubModel)] <- getmode(first_read_car_buy_df$SubModel)
```

#### 0 NULL or Blanks after replacing with mode
```{r}
length(first_read_car_buy_df$SubModel[first_read_car_buy_df$SubModel == ""|is.na(first_read_car_buy_df$SubModel)])
```


### 3. The Color column has 8 NULL or Blank values, which can be replaced with the mode of the value
```{r}
length(first_read_car_buy_df$Color[first_read_car_buy_df$Color == ""|is.na(first_read_car_buy_df$Color)])
```

```{r}
first_read_car_buy_df$Color[first_read_car_buy_df$Color == ""|is.na(first_read_car_buy_df$Color)] <- getmode(first_read_car_buy_df$Color)
```

#### 0 NULL or Blanks after replacing with mode
```{r}
length(first_read_car_buy_df$Color[first_read_car_buy_df$Color == ""|is.na(first_read_car_buy_df$Color)])
```


### 4. The Transmission column has 9 NULL or Blank values, which can be replaced with the mode of the value
```{r}
length(first_read_car_buy_df$Transmission[first_read_car_buy_df$Transmission == ""|is.na(first_read_car_buy_df$Transmission)])
```

```{r}
first_read_car_buy_df$Transmission[is.na(first_read_car_buy_df$Transmission) | first_read_car_buy_df$Transmission == "<NA>"] <-getmode(first_read_car_buy_df$Transmission)
```


#### 0 NULL or Blanks after replacing with mode
```{r}
length(first_read_car_buy_df$Transmission[first_read_car_buy_df$Transmission == ""| is.na(first_read_car_buy_df$Transmission)])
summary(first_read_car_buy_df$Transmission)
```

**Replacing Lower case Manual with MANUAL**
```{r}
first_read_car_buy_df$Transmission[first_read_car_buy_df$Transmission == "Manual"] <-"MANUAL"
```


### 5. The WheelType column has 3174 NULL or Blank values, which can be replaced with the mode of the value
```{r}
length(first_read_car_buy_df$WheelType[first_read_car_buy_df$WheelType == ""| is.na(first_read_car_buy_df$WheelType)])
```

```{r}
other_wheel_type <- c("OTHER")
#other_wheel_type <- as.factor(other_wheel_type)
mode(other_wheel_type)
first_read_car_buy_df$WheelType<-as.character(first_read_car_buy_df$WheelType)
```

```{r}
first_read_car_buy_df$WheelType[first_read_car_buy_df$WheelType == ""|is.na(first_read_car_buy_df$WheelType)] <-other_wheel_type
```


#### 0 NULL or Blanks after replacing with mode
```{r}
first_read_car_buy_df$WheelType<-as.factor(first_read_car_buy_df$WheelType)
length(first_read_car_buy_df$WheelType[first_read_car_buy_df$WheelType == ""|is.na(first_read_car_buy_df$WheelType)])
summary(first_read_car_buy_df$WheelType)
```

### 6. The Nationality column has 5 NULL or Blank values, which can be replaced with the mode of the value
```{r}
length(first_read_car_buy_df$Nationality[first_read_car_buy_df$Nationality == ""| is.na(first_read_car_buy_df$Nationality)])
```


```{r}
first_read_car_buy_df$Nationality[is.na(first_read_car_buy_df$Nationality)] <-getmode(first_read_car_buy_df$Nationality)
```


#### 0 NULL or Blanks after replacing with mode
```{r}
length(first_read_car_buy_df$Nationality[first_read_car_buy_df$Nationality == ""| is.na(first_read_car_buy_df$Nationality)])
summary(first_read_car_buy_df$Nationality)
```


### 7. The Size column has 5 NULL or Blank values, which can be replaced with the mode of the value
```{r}
length(first_read_car_buy_df$Size[first_read_car_buy_df$Size == ""| is.na(first_read_car_buy_df$Size)])
```

```{r}
first_read_car_buy_df$Size[is.na(first_read_car_buy_df$Size)] <-getmode(first_read_car_buy_df$Size)
```

#### 0 NULL or Blanks after replacing with mode
```{r}
length(first_read_car_buy_df$Size[first_read_car_buy_df$Size == ""| is.na(first_read_car_buy_df$Size)])
summary(first_read_car_buy_df$Size)
```


### 8. TopThreeAmericanName has 5 NULLS, replaced with mode
```{r}
length(first_read_car_buy_df$TopThreeAmericanName[first_read_car_buy_df$TopThreeAmericanName == ""| is.na(first_read_car_buy_df$TopThreeAmericanName)])
```

```{r}
first_read_car_buy_df$TopThreeAmericanName[is.na(first_read_car_buy_df$TopThreeAmericanName)|first_read_car_buy_df$TopThreeAmericanName == ""| first_read_car_buy_df$TopThreeAmericanName == "NULL"] <-getmode(first_read_car_buy_df$TopThreeAmericanName)
```

#### 0 NULL or Blanks after replacing with mode
```{r}
length(first_read_car_buy_df$TopThreeAmericanName[is.na(first_read_car_buy_df$TopThreeAmericanName)|first_read_car_buy_df$TopThreeAmericanName == ""| first_read_car_buy_df$TopThreeAmericanName == "NULL"])
#summary(first_read_car_buy_df$TopThreeAmericanName)
```


### 9. PRIMEUNIT has 69564 NULLS hence deleting these columns
```{r}
length(first_read_car_buy_df$PRIMEUNIT[first_read_car_buy_df$PRIMEUNIT == ""| is.na(first_read_car_buy_df$PRIMEUNIT)])
```


### 9. AUCGUART has 69564 NULLS hence deleting these columns
```{r}
length(first_read_car_buy_df$AUCGUART[is.na(first_read_car_buy_df$AUCGUART)|first_read_car_buy_df$AUCGUART == ""| first_read_car_buy_df$AUCGUART == "NULL"])
```



### 10. Checking structure of VNZIP1
```{r}
str(first_read_car_buy_df$VNZIP1)
str(first_read_car_buy_df$VNST)
```

### REMOVING UNIMPORTANT COLUMNS
```{r}
first_read_car_buy_df$WheelTypeID <- NULL
first_read_car_buy_df$VehYear <- NULL
first_read_car_buy_df$PurchDate <- NULL
first_read_car_buy_df$PRIMEUNIT <- NULL
first_read_car_buy_df$AUCGUART <- NULL
first_read_car_buy_df$BYRNO <- NULL
first_read_car_buy_df$RefId <- NULL
first_read_car_buy_df$VNZIP1 <- NULL
```

##### Checking DATAtypes to convert to required datatype if incorrect
```{r}
str(first_read_car_buy_df)
```

#### Converting all categorical variables to Factor datatype and Numerical Variables to numeric
```{r}
cat_var <- c('IsBadBuy', 'Auction', 'Make', 'Model', 'Trim', 'SubModel', 'Color', 'Transmission', 'WheelType', 'Nationality', 'Size', 'TopThreeAmericanName', 'VNST', 'IsOnlineSale')

num_var <- c('VehicleAge', 'VehOdo', 'MMRAcquisitionAuctionAveragePrice', 'MMRAcquisitionAuctionCleanPrice', 'MMRAcquisitionRetailAveragePrice', 'MMRAcquisitonRetailCleanPrice', 'MMRAcquisitonRetailCleanPrice', 'MMRCurrentAuctionAveragePrice', 'MMRCurrentAuctionCleanPrice', 'MMRCurrentRetailAveragePrice', 'MMRCurrentRetailCleanPrice', 'VehBCost', 'WarrantyCost')
```

```{r}
for (i in 1:length(cat_var)){
  first_read_car_buy_df[, cat_var[i]] <- as.factor(first_read_car_buy_df[, cat_var[i]])
}

for (i in 1:length(num_var)){
  first_read_car_buy_df[, num_var[i]] <- as.numeric(first_read_car_buy_df[, num_var[i]])
}
```


```{r}
str(first_read_car_buy_df)
```

#### Creating Dataframe of 4 only numeric cols: VehicleAge, VehOdo, VehBCost & WarrantyCost
```{r}
num_df <- first_read_car_buy_df[,c('VehicleAge','VehOdo','VehBCost','WarrantyCost')]
```

```{r}
#install.packages("gridExtra")
library(gridExtra)
```


#### HISTOGRAM of 4 numeric columns, Vehicle Age, Vehicle Odometer, Vehicle Cost & Warranty Cost
```{r}
hist_plot <- function(data_in, i) {
  data <- data.frame(x=data_in[[i]])
  p <- ggplot(data=data, aes(data[,1])) + 
    geom_histogram(bins = 30, col="red", aes(fill=..count..)) +
    xlab(colnames(data_in)[i]) +
    scale_fill_gradient("Count", low="green", high="red")
  return (p)
}
mygrid2 <- list()
for (i in 1:length(num_df)){
  myplot2 <- hist_plot(num_df, i)
  mygrid2 <- c(mygrid2, list(myplot2)) 
}
do.call("grid.arrange", c(mygrid2, ncol=2))
```

#### Creating Dataframe of all 8 auction & retail price columns
```{r}
num_df <- first_read_car_buy_df[,c('MMRAcquisitionAuctionAveragePrice','MMRAcquisitionAuctionCleanPrice','MMRAcquisitionRetailAveragePrice','MMRAcquisitonRetailCleanPrice','MMRCurrentAuctionAveragePrice','MMRCurrentAuctionCleanPrice','MMRCurrentRetailAveragePrice','MMRCurrentRetailCleanPrice')]
```



#### HISTOGRAM of 6 Auction & Retail Price Columns numeric columns
*Distributions are Uniform*
```{r}
hist_plot <- function(data_in, i) {
  data <- data.frame(x=data_in[[i]])
  p <- ggplot(data=data, aes(data[,1])) + 
    geom_histogram(bins = 30, col="red", aes(fill=..count..)) +
    xlab(colnames(data_in)[i]) +
    scale_fill_gradient("Count", low="green", high="red")
  return (p)
}
mygrid2 <- list()
for (i in 1:length(num_df)){
  myplot2 <- hist_plot(num_df, i)
  mygrid2 <- c(mygrid2, list(myplot2)) 
}
do.call("grid.arrange", c(mygrid2, ncol=2))
```

## Creating new Dataframe with NAs/NULLS removed

```{r}
car_buy_NA_rem_df <- first_read_car_buy_df
```


#### 1. There are 0 outliers in Vehicle Age column
```{r}
car_buy_NA_rem_df$VehicleAgeZ <- scale(car_buy_NA_rem_df$VehicleAge)
nrow(car_buy_NA_rem_df[abs(car_buy_NA_rem_df$VehicleAgeZ)>3,])
```

#### 2. There are 194 outliers in Vehicle Odometer column which needs to be winsorized
```{r}
car_buy_NA_rem_df$VehOdoZ <- scale(car_buy_NA_rem_df$VehOdo)
nrow(car_buy_NA_rem_df[abs(car_buy_NA_rem_df$VehOdoZ)>3,])
```

```{r}
car_buy_NA_rem_df$VehOdo[car_buy_NA_rem_df$VehOdoZ<=-3]<-max(car_buy_NA_rem_df$VehOdo[car_buy_NA_rem_df$VehOdoZ<=-3])
```

#### AFTER Winsorizing vehicle odometer column
```{r}
summary(car_buy_NA_rem_df$VehOdo)
```

#### 3. There are 48 outliers in Vehicle Cost column
```{r}
car_buy_NA_rem_df$VehBCostZ <- scale(car_buy_NA_rem_df$VehBCost)
nrow(car_buy_NA_rem_df[abs(car_buy_NA_rem_df$VehBCostZ)>3,])
```

##### Winsorizing 
```{r}
car_buy_NA_rem_df$VehBCost[car_buy_NA_rem_df$VehBCostZ>3]<-min(car_buy_NA_rem_df$VehBCost[car_buy_NA_rem_df$VehBCostZ>3])
```

#### AFTER Winsorizing vehicle Cost column
```{r}
summary(car_buy_NA_rem_df$VehBCost)
```

#### 4. There are 680 outliers in WarrantyCost column which needs to be winsorized
```{r}
car_buy_NA_rem_df$WarrantyCostZ <- scale(car_buy_NA_rem_df$WarrantyCost)
nrow(car_buy_NA_rem_df[abs(car_buy_NA_rem_df$WarrantyCostZ)>3,])
```

```{r}
summary(car_buy_NA_rem_df$WarrantyCost)
```

```{r}
car_buy_NA_rem_df$WarrantyCost[car_buy_NA_rem_df$WarrantyCostZ>3]<-min(car_buy_NA_rem_df$WarrantyCost[car_buy_NA_rem_df$WarrantyCostZ>3])
```

#### AFTER Winsorizing WarrantyCost column
```{r}
summary(car_buy_NA_rem_df$WarrantyCost)
```

```{r}
num_df <- car_buy_NA_rem_df[,c('VehicleAge','VehOdo','VehBCost','WarrantyCost')]
```

#### HISTOGRAM of 4 numeric columns (Vehicle Age, Vehicle Odometer, Vehicle Cost & Warranty Cost) after Winsorizing outliers
*Reduced the skewness*
```{r}
library(ggplot2)
hist_plot <- function(data_in, i) {
  data <- data.frame(x=data_in[[i]])
  p <- ggplot(data=data, aes(data[,1])) + 
    geom_histogram(bins = 30, col="red", aes(fill=..count..)) +
    xlab(colnames(data_in)[i]) +
    scale_fill_gradient("Count", low="green", high="red")
  return (p)
}
mygrid2 <- list()
for (i in 1:length(num_df)){
  myplot2 <- hist_plot(num_df, i)
  mygrid2 <- c(mygrid2, list(myplot2)) 
}
do.call("grid.arrange", c(mygrid2, ncol=2))
```

```{r}
car_buy_NA_rem_df$Transmission[car_buy_NA_rem_df$Transmission==""] <- getmode(car_buy_NA_rem_df$Transmission)
car_buy_NA_rem_df$Transmission <- as.character(car_buy_NA_rem_df$Transmission)
car_buy_NA_rem_df$Transmission <- as.factor(car_buy_NA_rem_df$Transmission)
```


```{r}
str(car_buy_NA_rem_df)
summary(car_buy_NA_rem_df)
```

#### 1. IMPUTING NAs for Numeric column with MEAN of the column
```{r}
car_buy_NA_rem_df$MMRAcquisitionAuctionAveragePrice[is.na(car_buy_NA_rem_df$MMRAcquisitionAuctionAveragePrice)] <- mean(car_buy_NA_rem_df$MMRAcquisitionAuctionAveragePrice, na.rm = TRUE)

```


```{r}
length(car_buy_NA_rem_df$MMRAcquisitionAuctionAveragePrice[is.na(car_buy_NA_rem_df$MMRAcquisitionAuctionAveragePrice)])
```

#### 2. IMPUTING NAs for Numeric columns with MEAN of the column

```{r}
length(car_buy_NA_rem_df$MMRAcquisitionAuctionCleanPrice[is.na(car_buy_NA_rem_df$MMRAcquisitionAuctionCleanPrice)])
```


```{r}
car_buy_NA_rem_df$MMRAcquisitionAuctionCleanPrice[is.na(car_buy_NA_rem_df$MMRAcquisitionAuctionCleanPrice)] <- mean(car_buy_NA_rem_df$MMRAcquisitionAuctionCleanPrice, na.rm = TRUE)

```


```{r}
length(car_buy_NA_rem_df$MMRAcquisitionAuctionCleanPrice[is.na(car_buy_NA_rem_df$MMRAcquisitionAuctionCleanPrice)])
```

#### 3. IMPUTING NAs for Numeric columns with MEAN of the column

```{r}
length(car_buy_NA_rem_df$MMRAcquisitionRetailAveragePrice[is.na(car_buy_NA_rem_df$MMRAcquisitionRetailAveragePrice)])
```


```{r}
car_buy_NA_rem_df$MMRAcquisitionRetailAveragePrice[is.na(car_buy_NA_rem_df$MMRAcquisitionRetailAveragePrice)] <- mean(car_buy_NA_rem_df$MMRAcquisitionRetailAveragePrice, na.rm = TRUE)

```


```{r}
length(car_buy_NA_rem_df$MMRAcquisitionRetailAveragePrice[is.na(car_buy_NA_rem_df$MMRAcquisitionRetailAveragePrice)])
```

#### 4. IMPUTING NAs for Numeric columns with MEAN of the column

```{r}
length(car_buy_NA_rem_df$MMRAcquisitonRetailCleanPrice[is.na(car_buy_NA_rem_df$MMRAcquisitonRetailCleanPrice)])
```


```{r}
car_buy_NA_rem_df$MMRAcquisitonRetailCleanPrice[is.na(car_buy_NA_rem_df$MMRAcquisitonRetailCleanPrice)] <- mean(car_buy_NA_rem_df$MMRAcquisitonRetailCleanPrice, na.rm = TRUE)

```


```{r}
length(car_buy_NA_rem_df$MMRAcquisitonRetailCleanPrice[is.na(car_buy_NA_rem_df$MMRAcquisitonRetailCleanPrice)])
```

#### 5. IMPUTING NAs for Numeric columns with MEAN of the column

```{r}
length(car_buy_NA_rem_df$MMRCurrentAuctionAveragePrice[is.na(car_buy_NA_rem_df$MMRCurrentAuctionAveragePrice)])
```


```{r}
car_buy_NA_rem_df$MMRCurrentAuctionAveragePrice[is.na(car_buy_NA_rem_df$MMRCurrentAuctionAveragePrice)] <- mean(car_buy_NA_rem_df$MMRCurrentAuctionAveragePrice, na.rm = TRUE)

```


```{r}
length(car_buy_NA_rem_df$MMRAcquisitonRetailCleanPrice[is.na(car_buy_NA_rem_df$MMRAcquisitonRetailCleanPrice)])
```

#### 6. IMPUTING NAs for Numeric columns with MEAN of the column

```{r}
length(car_buy_NA_rem_df$MMRCurrentAuctionCleanPrice[is.na(car_buy_NA_rem_df$MMRCurrentAuctionCleanPrice)])
```

```{r}
car_buy_NA_rem_df$MMRCurrentAuctionCleanPrice[is.na(car_buy_NA_rem_df$MMRCurrentAuctionCleanPrice)] <- mean(car_buy_NA_rem_df$MMRCurrentAuctionCleanPrice, na.rm = TRUE)
```

```{r}
length(car_buy_NA_rem_df$MMRAcquisitonRetailCleanPrice[is.na(car_buy_NA_rem_df$MMRAcquisitonRetailCleanPrice)])
```

#### 7. IMPUTING NAs for Numeric columns with MEAN of the column

```{r}
length(car_buy_NA_rem_df$MMRCurrentRetailAveragePrice[is.na(car_buy_NA_rem_df$MMRCurrentRetailAveragePrice)])
```

```{r}
car_buy_NA_rem_df$MMRCurrentRetailAveragePrice[is.na(car_buy_NA_rem_df$MMRCurrentRetailAveragePrice)] <- mean(car_buy_NA_rem_df$MMRCurrentRetailAveragePrice, na.rm = TRUE)
```

```{r}
length(car_buy_NA_rem_df$MMRCurrentRetailAveragePrice[is.na(car_buy_NA_rem_df$MMRCurrentRetailAveragePrice)])
```

#### 8. IMPUTING NAs for Numeric columns with MEAN of the column

```{r}
length(car_buy_NA_rem_df$MMRCurrentRetailCleanPrice[is.na(car_buy_NA_rem_df$MMRCurrentRetailCleanPrice)])
```

```{r}
car_buy_NA_rem_df$MMRCurrentRetailCleanPrice[is.na(car_buy_NA_rem_df$MMRCurrentRetailCleanPrice)] <- mean(car_buy_NA_rem_df$MMRCurrentRetailCleanPrice, na.rm = TRUE)
```

```{r}
length(car_buy_NA_rem_df$MMRCurrentRetailCleanPrice[is.na(car_buy_NA_rem_df$MMRCurrentRetailCleanPrice)])
```

#### FINAL CLEANED DATAFRAME
```{r}
car_buy_clean_df <- car_buy_NA_rem_df
car_buy_clean_df$VehBCostZ <- NULL
car_buy_clean_df$VehicleAgeZ <- NULL
car_buy_clean_df$VehOdoZ <- NULL
car_buy_clean_df$WarrantyCostZ <- NULL
```

```{r}
car_buy_clean_df$Make <- as.character(car_buy_clean_df$Make)
car_buy_clean_df$Make <- as.factor(car_buy_clean_df$Make)

car_buy_clean_df$Model <- as.character(car_buy_clean_df$Model)
car_buy_clean_df$Model <- as.factor(car_buy_clean_df$Model)

car_buy_clean_df$Trim <- as.character(car_buy_clean_df$Trim)
car_buy_clean_df$Trim <- as.factor(car_buy_clean_df$Trim)

car_buy_clean_df$SubModel <- as.character(car_buy_clean_df$SubModel)
car_buy_clean_df$SubModel <- as.factor(car_buy_clean_df$SubModel)

car_buy_clean_df$Color <- as.character(car_buy_clean_df$Color)
car_buy_clean_df$Color <- as.factor(car_buy_clean_df$Color)

car_buy_clean_df$Nationality <- as.character(car_buy_clean_df$Nationality)
car_buy_clean_df$Nationality <- as.factor(car_buy_clean_df$Nationality)

car_buy_clean_df$Size <- as.character(car_buy_clean_df$Size)
car_buy_clean_df$Size <- as.factor(car_buy_clean_df$Size)

car_buy_clean_df$TopThreeAmericanName <- as.character(car_buy_clean_df$TopThreeAmericanName)
car_buy_clean_df$TopThreeAmericanName <- as.factor(car_buy_clean_df$TopThreeAmericanName)

car_buy_clean_df$VNST <- as.character(car_buy_clean_df$VNST)
car_buy_clean_df$VNST <- as.factor(car_buy_clean_df$VNST)
```


### Viewing Structure and Summary of final cleaned dataset
```{r}
str(car_buy_clean_df)
summary(car_buy_clean_df)
```


```{r}
#### Renaming columns
colnames(car_buy_clean_df) <- c("IsBadBuy","Auction","VehicleAge","Make","Model","Trim","SubModel","Color","Transmission","WheelType","VehOdo","Nationality","Size","TopThreeAmericanName","MMRAcqAucAvgPrice","MMRAcqAucCleanPrice","MMRAcqRetailAvgPrice","MMRAcqRetailCleanPrice","MMRCurrAucAvgPrice","MMRCurrAucCleanPrice","MMRCurrRetailAvgPrice","MMRCurrRetailCleanPrice","VNST","VehBCost","IsOnlineSale","WarrantyCost")
```

```{r}
str(car_buy_clean_df)
```

```{r}
summary(car_buy_clean_df)
```

```{r}
#testdf <- readRDS(file = "car_buy_clean_df.Rda")

apply(is.na(car_buy_clean_df), 2, sum)
```


```{r}
saveRDS(car_buy_clean_df,file="car_buy_clean_df.Rda")
```


```{r}
write.csv(car_buy_clean_df,"car_buy_clean_df.csv",row.names = FALSE)
```





























