---
title: "Exploratory Data Analysis"
author: "Tejas Patil"
date: "2020 M04 12"
output: html_document
---
```{r}
setwd("C:/Users/bhavi/OneDrive/Desktop/SYR ADS/Sem 2/IST_707_Data_Analytics/Project")

```

#### READING CLEANED DATA into DF
```{r}
car_buy_clean_df <- readRDS(file = "car_buy_clean_df.Rda")

```


```{r}
library(ggplot2)
```


#### Bar graph for Plotting Target variable vs Nationality
**</b> The % of Bad Buy's are equal amongst all the nationalities and hence Nationality may not be an important feature**
```{r}
ggplot(car_buy_clean_df, aes(IsBadBuy, group = Nationality)) + 
  geom_bar(aes(y = ..prop.., fill = IsBadBuy), stat="count") +
  geom_text(aes(label = scales::percent(..prop..),
                y = ..prop..), stat = "count", vjust = -0.5) +
  labs(y = "Percent", fill = "IsBadBuy") +
  facet_grid(~Nationality) + 
  scale_y_continuous(labels = scales::percent)
```

#### Bar graph for Target variable vs Transmission
**</b> Both AUTO & MANUAL Transmission have approximately equal proportion of Bad Buys**
```{r}
library(ggplot2)
transmission_bad_buy_plot <- ggplot(car_buy_clean_df, aes(IsBadBuy, group = Transmission)) + 
  geom_bar(aes(y = ..prop.., fill = IsBadBuy), stat="count",fill = "#FF6666") +
  geom_text(aes(label = scales::percent(..prop..),
                y = ..prop..), stat = "count", vjust = -0.5) +
  labs(y = "Percent", fill = "IsBadBuy") + ggtitle("Transmission VS % of Bad Buys")+
  facet_grid(~Transmission) + 
  scale_y_continuous(labels = scales::percent)

transmission_bad_buy_plot
```


```{r}
car_count_by_transmission <- car_buy_clean_df %>%
      group_by(Transmission,as.factor(IsBadBuy))%>%
      summarise(n())
colnames(car_count_by_transmission) <- c('Transmission','IsBadBuy','count_cars')

transmission_bad_buy_plot <- ggplot(car_count_by_transmission,aes(fill = IsBadBuy,x=Transmission,y=count_cars))+geom_bar(position="stack",stat = "identity")+
             xlab("Transmission")+ ylab("Number of cars sold")+ ggtitle("Transmission VS Number of Cars sold by Bad Buy categories")+ theme(axis.text.x = element_text(angle = 90, hjust = 1))
transmission_bad_buy_plot
```


#### Bar graph for Target variable vs Auction
**</b> Auction ADESA has slightly higher % of bad buys**
```{r}
ggplot(car_buy_clean_df, aes(IsBadBuy, group = Auction)) + 
  geom_bar(aes(y = ..prop.., fill = IsBadBuy), stat="count") +
  geom_text(aes(label = scales::percent(..prop..),
                y = ..prop..), stat = "count", vjust = -0.5) +
  labs(y = "Percent", fill = "IsBadBuy") +
  facet_grid(~Auction) + 
  scale_y_continuous(labels = scales::percent)
```

#### Bar graph for Target variable vs TopThreeAmericanNames
**</b>The company Ford higher % of bad buys in comparison to other car companies**
```{r}
ggplot(car_buy_clean_df, aes(IsBadBuy, group = TopThreeAmericanName)) + 
  geom_bar(aes(y = ..prop.., fill = IsBadBuy), stat="count") +
  geom_text(aes(label = scales::percent(..prop..),
                y = ..prop..), stat = "count", vjust = -0.5) +
  labs(y = "Percent", fill = "IsBadBuy") +
  facet_grid(~TopThreeAmericanName) + 
  scale_y_continuous(labels = scales::percent)
```

#### SIZE VS Proportion of Bad Buys
**</br> Size does not play a significant role in determining whether car is a good buy or bad buy**
```{r}
#library(tidyverse)
car_count_by_size <- car_buy_clean_df %>%
      group_by(Size,as.factor(IsBadBuy))%>%
      summarise(n())
colnames(car_count_by_size) <- c('Size','IsBadBuy','count_cars')

size_bad_buy_plot <- ggplot(car_count_by_size,aes(fill = IsBadBuy,x=Size,y=count_cars))+geom_bar(position="stack",stat = "identity")+
             xlab("Sizes")+ ylab("Number of cars sold")+ ggtitle("Size VS proportion of Bad Buys")+ theme(axis.text.x = element_text(angle = 90, hjust = 1))
size_bad_buy_plot
```

#### The Wheel Type OTHER has a high proportion of Bad Buys
```{r}

library(tidyverse)
car_count_by_WheelType <- car_buy_clean_df %>%
      group_by(WheelType,as.factor(IsBadBuy))%>%
      summarise(n())
colnames(car_count_by_WheelType) <- c('WheelType','IsBadBuy','count_cars')

WheelType_bad_buy_plot <- ggplot(car_count_by_WheelType,aes(fill = IsBadBuy,x=WheelType,y=count_cars))+geom_bar(position="stack",stat = "identity")+
             xlab("Wheel Type")+ ylab("Number of cars sold")+ ggtitle("Wheel Type VS Number of Cars sold by Bad Buy categories")+ theme(axis.text.x = element_text(angle = 90, hjust = 1))
WheelType_bad_buy_plot

```


#### There is a high % of Bad Buys amongst "OTHER" wheel type
```{r}
library(ggplot2)
ggplot(car_buy_clean_df, aes(IsBadBuy, group = WheelType)) + 
  geom_bar(aes(y = ..prop.., fill = IsBadBuy), stat="count") +
  geom_text(aes(label = scales::percent(..prop..),
                y = ..prop..), stat = "count", vjust = -0.5) +
  labs(y = "Percent", fill = "IsBadBuy") +
  facet_grid(~WheelType) + 
  scale_y_continuous(labels = scales::percent)
```


#### There is not much significant difference in the % of bad buys amongst different makes
```{r}
car_count_by_make <- car_buy_clean_df %>%
      group_by(Make,as.factor(IsBadBuy))%>%
      summarise(n())
colnames(car_count_by_make) <- c('Make','IsBadBuy','count_cars')

make_bad_buy_plot <- ggplot(car_count_by_make,aes(fill = IsBadBuy,x=Make,y=count_cars))+geom_bar(position="stack",stat = "identity")+
             xlab("Make")+ ylab("Number of cars sold")+ ggtitle("Make VS proportion of Bad Buys")+ theme(axis.text.x = element_text(angle = 90, hjust = 1))
make_bad_buy_plot

```


```{r}
ggplot(data = car_buy_clean_df, mapping = aes(x = WheelType, y = as.integer
                                      (car_buy_clean_df$IsBadBuy))) +
  stat_summary(fun.y = "median", colour = "red", size = 5, geom = "point") +
  stat_summary(fun.y = "mean", colour = "blue", size = 5, geom = "point") +
  theme(axis.text.x=element_text(angle=90))

```

#### We can observe that Florida and Texas states have the highest number of car sales and hence highest proportion of Bad Buys
```{r}
car_count_by_VNST <- car_buy_clean_df %>%
      group_by(VNST,as.factor(IsBadBuy))%>%
      summarise(n())
colnames(car_count_by_VNST) <- c('VNST','IsBadBuy','count_cars')

VNST_bad_buy_plot <- ggplot(car_count_by_VNST,aes(fill = IsBadBuy,x=VNST,y=count_cars))+geom_bar(position="stack",stat = "identity")+
             xlab("State")+ ylab("Number of cars sold")+ ggtitle("VNST VS Number of Cars sold by Bad Buy categories")+ theme(axis.text.x = element_text(angle = 90, hjust = 1))
VNST_bad_buy_plot
```

```{r}
ggplot(data = car_buy_clean_df, mapping = aes(x = VNST, y = as.integer
                                      (car_buy_clean_df$IsBadBuy))) +
  stat_summary(fun.y = "median", colour = "red", size = 5, geom = "point") +
  stat_summary(fun.y = "mean", colour = "blue", size = 5, geom = "point") +
  theme(axis.text.x=element_text(angle=90))
```


#### Plotting Vehicle Age with Target Variable 
**</b> The % of bad buy increases with vehicle age**
```{r}
car_count_by_VehicleAge <- car_buy_clean_df[car_buy_clean_df$VehicleAge != 0,]
car_count_by_VehicleAge$VehicleAge <- as.factor(car_count_by_VehicleAge$VehicleAge)

Agevsbadbuy<-ggplot(car_count_by_VehicleAge, aes(IsBadBuy, group = VehicleAge)) + 
  geom_bar(aes(y = ..prop.., fill = IsBadBuy), stat="count",fill = "#FF6666") +
  geom_text(aes(label = scales::percent(..prop..),
                y = ..prop..), stat = "count", vjust = -0.5) +
  labs(y = "Percent",fill = "IsBadBuy") + ggtitle("% of Bad Buy VS Vehicle Age")+
  facet_grid(~VehicleAge) + 
  scale_y_continuous(labels = scales::percent)
Agevsbadbuy
```

#### Plotting Vehicle Odometer with Target Variable
**</br> We can observe that % of Bad Buys increases with higher vehicle odometer reading groups**
```{r}
car_count_by_VehicleAge$VehOdoGroups <-cut(car_count_by_VehicleAge$VehOdo, breaks = c(quantile(car_count_by_VehicleAge$VehOdo, probs = c(0,0.25,0.5,0.75,1))),
     labels = c(str_c(quantile(car_count_by_VehicleAge$VehOdo,probs = 0),quantile(car_count_by_VehicleAge$VehOdo,probs = 0.25),sep = " to "),str_c(quantile(car_count_by_VehicleAge$VehOdo,probs = 0.25),quantile(car_count_by_VehicleAge$VehOdo,probs = 0.5),sep = " to "),str_c(quantile(car_count_by_VehicleAge$VehOdo,probs = 0.5),quantile(car_count_by_VehicleAge$VehOdo,probs = 0.75),sep = " to "),str_c(quantile(car_count_by_VehicleAge$VehOdo,probs = 0.75),quantile(car_count_by_VehicleAge$VehOdo,probs = 1),sep = " to ")), right = FALSE, include.lowest=TRUE)
car_count_by_VehicleAge$VehOdoGroups<-as.factor(car_count_by_VehicleAge$VehOdoGroups)


Odovsbadbuy<-ggplot(car_count_by_VehicleAge, aes(IsBadBuy, group = VehOdoGroups)) + 
  geom_bar(aes(y = ..prop.., fill = IsBadBuy), stat="count",fill = "#FF6666") +
  geom_text(aes(label = scales::percent(..prop..),
                y = ..prop..), stat = "count", vjust = -0.5) +
  labs(y = "Percent",fill = "IsBadBuy") + ggtitle("% of Bad Buy VS Vehicle Odometer Reading groups")+
  facet_grid(~VehOdoGroups) + 
  scale_y_continuous(labels = scales::percent)
Odovsbadbuy
```

#### Plotting VehBCost - Acquisition cost paid for the vehicle with Target Variable
**</br> We can observe that % of Bad Buys is higher for lower Acquistion cost groups**
```{r}
car_count_by_VehicleAge$VehBCostGroups <-cut(car_count_by_VehicleAge$VehBCost, breaks = c(quantile(car_count_by_VehicleAge$VehBCost, probs = c(0,0.25,0.5,0.75,1))),
     labels = c(str_c(quantile(car_count_by_VehicleAge$VehBCost,probs = 0),quantile(car_count_by_VehicleAge$VehBCost,probs = 0.25),sep = " to "),str_c(quantile(car_count_by_VehicleAge$VehBCost,probs = 0.25),quantile(car_count_by_VehicleAge$VehBCost,probs = 0.5),sep = " to "),str_c(quantile(car_count_by_VehicleAge$VehBCost,probs = 0.5),quantile(car_count_by_VehicleAge$VehBCost,probs = 0.75),sep = " to "),str_c(quantile(car_count_by_VehicleAge$VehBCost,probs = 0.75),quantile(car_count_by_VehicleAge$VehBCost,probs = 1),sep = " to ")), right = FALSE, include.lowest=TRUE)
car_count_by_VehicleAge$VehBCostGroups<-as.factor(car_count_by_VehicleAge$VehBCostGroups)


VehBCostvsbadbuy<-ggplot(car_count_by_VehicleAge, aes(IsBadBuy, group = VehBCostGroups)) + 
  geom_bar(aes(y = ..prop.., fill = IsBadBuy), stat="count",fill = "#FF6666") +
  geom_text(aes(label = scales::percent(..prop..),
                y = ..prop..), stat = "count", vjust = -0.5) +
  labs(y = "Percent",fill = "IsBadBuy") + ggtitle("% of Bad Buy VS Vehicle B Cost Reading groups")+
  facet_grid(~VehBCostGroups) + 
  scale_y_continuous(labels = scales::percent)
VehBCostvsbadbuy
```


#### Plotting WarrantyCost with Target Variable
**</br> We can observe that %(proportion) of Bad Buys increases for higher Warranty Costs**
```{r}
library(stringr)
library(ggplot2)
car_count_by_VehicleAge$WarrantyCostGroups <-cut(car_count_by_VehicleAge$WarrantyCost, breaks = c(quantile(car_count_by_VehicleAge$WarrantyCost, probs = c(0,0.25,0.5,0.75,1))),
     labels = c(str_c(quantile(car_count_by_VehicleAge$WarrantyCost,probs = 0),quantile(car_count_by_VehicleAge$WarrantyCost,probs = 0.25),sep = " to "),str_c(quantile(car_count_by_VehicleAge$WarrantyCost,probs = 0.25),quantile(car_count_by_VehicleAge$WarrantyCost,probs = 0.5),sep = " to "),str_c(quantile(car_count_by_VehicleAge$WarrantyCost,probs = 0.5),quantile(car_count_by_VehicleAge$WarrantyCost,probs = 0.75),sep = " to "),str_c(quantile(car_count_by_VehicleAge$WarrantyCost,probs = 0.75),quantile(car_count_by_VehicleAge$WarrantyCost,probs = 1),sep = " to ")), right = FALSE, include.lowest=TRUE)
car_count_by_VehicleAge$WarrantyCostGroups<-as.factor(car_count_by_VehicleAge$WarrantyCostGroups)


WarrantyCostvsbadbuy<- ggplot(car_count_by_VehicleAge, aes(IsBadBuy, group = WarrantyCostGroups)) + 
  geom_bar(aes(y = ..prop.., fill = IsBadBuy), stat="count",fill = "#FF6666") +
  geom_text(aes(label = scales::percent(..prop..),
                y = ..prop..), stat = "count", vjust = -0.5) +
  labs(y = "Percent",fill = "IsBadBuy") + ggtitle("% of Bad Buy and Good Buy VS Warranty Cost ranges")+
  facet_grid(~WarrantyCostGroups) + 
  scale_y_continuous(labels = scales::percent)
WarrantyCostvsbadbuy
```


```{r}
ggplot(car_count_by_VehicleAge, aes(IsBadBuy, group = IsOnlineSale)) + 
  geom_bar(aes(y = ..prop.., fill = IsBadBuy), stat="count") +
  geom_text(aes(label = scales::percent(..prop..),
                y = ..prop..), stat = "count", vjust = -0.5) +
  labs(y = "Percent",fill = "IsBadBuy") + ggtitle("% of Bad Buy VS Online/Offline Sales")+
  facet_grid(~IsOnlineSale) + 
  scale_y_continuous(labels = scales::percent)
```

#### 1. % Bad Buy is higher for lower acquistion Auction average prices
**</br> The Proportion of Bad Buys is lower for higher acquisition average price groups**
```{r}
car_count_by_VehicleAge$MMRAcqAucAvgPriceGroups <-cut(car_count_by_VehicleAge$MMRAcqAucAvgPrice, breaks = c(quantile(car_count_by_VehicleAge$MMRAcqAucAvgPrice, probs = c(0,0.25,0.5,0.75,1))),
     labels = c(str_c(quantile(car_count_by_VehicleAge$MMRAcqAucAvgPrice,probs = 0),quantile(car_count_by_VehicleAge$MMRAcqAucAvgPrice,probs = 0.25),sep = " to "),str_c(quantile(car_count_by_VehicleAge$MMRAcqAucAvgPrice,probs = 0.25),quantile(car_count_by_VehicleAge$MMRAcqAucAvgPrice,probs = 0.5),sep = " to "),str_c(quantile(car_count_by_VehicleAge$MMRAcqAucAvgPrice,probs = 0.5),quantile(car_count_by_VehicleAge$MMRAcqAucAvgPrice,probs = 0.75),sep = " to "),str_c(quantile(car_count_by_VehicleAge$MMRAcqAucAvgPrice,probs = 0.75),quantile(car_count_by_VehicleAge$MMRAcqAucAvgPrice,probs = 1),sep = " to ")), right = FALSE, include.lowest=TRUE)
car_count_by_VehicleAge$MMRAcqAucAvgPriceGroups<-as.factor(car_count_by_VehicleAge$MMRAcqAucAvgPriceGroups)


acq_auc_avg_price <- ggplot(car_count_by_VehicleAge, aes(IsBadBuy, group = MMRAcqAucAvgPriceGroups)) + 
  geom_bar(aes(y = ..prop.., fill = IsBadBuy), stat="count",fill = "#FF6666") +
  geom_text(aes(label = scales::percent(..prop..),
                y = ..prop..), stat = "count", vjust = -0.5) +
  labs(y = "Percent",fill = "IsBadBuy") + ggtitle("% of Bad Buy VS MMRAcquisitionAuctionAveragePrice groups")+
  facet_grid(~MMRAcqAucAvgPriceGroups) + 
  scale_y_continuous(labels = scales::percent)
acq_auc_avg_price
```

#### 2. Proportion of Bad Buy is lower for higher acquistion auction clean prices
```{r}
car_count_by_VehicleAge$MMRAcqAucCleanPriceGroups <-cut(car_count_by_VehicleAge$MMRAcqAucCleanPrice, breaks = c(quantile(car_count_by_VehicleAge$MMRAcqAucCleanPrice, probs = c(0,0.25,0.5,0.75,1))),
     labels = c(str_c(quantile(car_count_by_VehicleAge$MMRAcqAucCleanPrice,probs = 0),quantile(car_count_by_VehicleAge$MMRAcqAucCleanPrice,probs = 0.25),sep = " to "),str_c(quantile(car_count_by_VehicleAge$MMRAcqAucCleanPrice,probs = 0.25),quantile(car_count_by_VehicleAge$MMRAcqAucCleanPrice,probs = 0.5),sep = " to "),str_c(quantile(car_count_by_VehicleAge$MMRAcqAucCleanPrice,probs = 0.5),quantile(car_count_by_VehicleAge$MMRAcqAucCleanPrice,probs = 0.75),sep = " to "),str_c(quantile(car_count_by_VehicleAge$MMRAcqAucCleanPrice,probs = 0.75),quantile(car_count_by_VehicleAge$MMRAcqAucCleanPrice,probs = 1),sep = " to ")), right = FALSE, include.lowest=TRUE)
car_count_by_VehicleAge$MMRAcqAucCleanPriceGroups<-as.factor(car_count_by_VehicleAge$MMRAcqAucCleanPriceGroups)


acq_auc_clean_price<-ggplot(car_count_by_VehicleAge, aes(IsBadBuy, group = MMRAcqAucCleanPriceGroups)) + 
  geom_bar(aes(y = ..prop.., fill = IsBadBuy), stat="count",fill = "#FF6666") +
  geom_text(aes(label = scales::percent(..prop..),
                y = ..prop..), stat = "count", vjust = -0.5) +
  labs(y = "Percent",fill = "IsBadBuy") + ggtitle("% of Bad Buy VS MMRAcquisitionAuctionCleanPrice groups")+
  facet_grid(~MMRAcqAucCleanPriceGroups) + 
  scale_y_continuous(labels = scales::percent)
acq_auc_clean_price
```


#### 3. No Concrete conclusion can be drawn for MMRAcqRetailAvgPriceGroups
```{r}
car_count_by_VehicleAge$MMRAcqRetailAvgPriceGroups <-cut(car_count_by_VehicleAge$MMRAcqRetailAvgPrice, breaks = c(quantile(car_count_by_VehicleAge$MMRAcqRetailAvgPrice, probs = c(0,0.25,0.5,0.75,1))),
     labels = c(str_c(quantile(car_count_by_VehicleAge$MMRAcqRetailAvgPrice,probs = 0),quantile(car_count_by_VehicleAge$MMRAcqRetailAvgPrice,probs = 0.25),sep = " to "),str_c(quantile(car_count_by_VehicleAge$MMRAcqRetailAvgPrice,probs = 0.25),quantile(car_count_by_VehicleAge$MMRAcqRetailAvgPrice,probs = 0.5),sep = " to "),str_c(quantile(car_count_by_VehicleAge$MMRAcqRetailAvgPrice,probs = 0.5),quantile(car_count_by_VehicleAge$MMRAcqRetailAvgPrice,probs = 0.75),sep = " to "),str_c(quantile(car_count_by_VehicleAge$MMRAcqRetailAvgPrice,probs = 0.75),quantile(car_count_by_VehicleAge$MMRAcqRetailAvgPrice,probs = 1),sep = " to ")), right = FALSE, include.lowest=TRUE)
car_count_by_VehicleAge$MMRAcqRetailAvgPriceGroups<-as.factor(car_count_by_VehicleAge$MMRAcqRetailAvgPriceGroups)


ggplot(car_count_by_VehicleAge, aes(IsBadBuy, group = MMRAcqRetailAvgPriceGroups)) + 
  geom_bar(aes(y = ..prop.., fill = IsBadBuy), stat="count") +
  geom_text(aes(label = scales::percent(..prop..),
                y = ..prop..), stat = "count", vjust = -0.5) +
  labs(y = "Percent",fill = "IsBadBuy") + ggtitle("% of Bad Buy VS MMRAcquisitionRetailAveragePrice groups")+
  facet_grid(~MMRAcqRetailAvgPriceGroups) + 
  scale_y_continuous(labels = scales::percent)

```


#### 4. No Concrete conclusion can be drawn for MMRAcqRetailCleanPriceGroups
```{r}
car_count_by_VehicleAge$MMRAcqRetailCleanPriceGroups <-cut(car_count_by_VehicleAge$MMRAcqRetailCleanPrice, breaks = c(quantile(car_count_by_VehicleAge$MMRAcqRetailCleanPrice, probs = c(0,0.25,0.5,0.75,1))),
     labels = c(str_c(quantile(car_count_by_VehicleAge$MMRAcqRetailCleanPrice,probs = 0),quantile(car_count_by_VehicleAge$MMRAcqRetailCleanPrice,probs = 0.25),sep = " to "),str_c(quantile(car_count_by_VehicleAge$MMRAcqRetailCleanPrice,probs = 0.25),quantile(car_count_by_VehicleAge$MMRAcqRetailCleanPrice,probs = 0.5),sep = " to "),str_c(quantile(car_count_by_VehicleAge$MMRAcqRetailCleanPrice,probs = 0.5),quantile(car_count_by_VehicleAge$MMRAcqRetailCleanPrice,probs = 0.75),sep = " to "),str_c(quantile(car_count_by_VehicleAge$MMRAcqRetailCleanPrice,probs = 0.75),quantile(car_count_by_VehicleAge$MMRAcqRetailCleanPrice,probs = 1),sep = " to ")), right = FALSE, include.lowest=TRUE)
car_count_by_VehicleAge$MMRAcqRetailAvgPriceGroups<-as.factor(car_count_by_VehicleAge$MMRAcqRetailAvgPriceGroups)


ggplot(car_count_by_VehicleAge, aes(IsBadBuy, group = MMRAcqRetailCleanPriceGroups)) + 
  geom_bar(aes(y = ..prop.., fill = IsBadBuy), stat="count") +
  geom_text(aes(label = scales::percent(..prop..),
                y = ..prop..), stat = "count", vjust = -0.5) +
  labs(y = "Percent",fill = "IsBadBuy") + ggtitle("% of Bad Buy VS MMRAcquisitionRetailCleanPrice groups")+
  facet_grid(~MMRAcqRetailCleanPriceGroups) + 
  scale_y_continuous(labels = scales::percent)

```

#### 5. Proportion of Bad Buy decreases with increase in Current Auction Average Price
```{r}
car_count_by_VehicleAge$MMRCurrAucAvgPriceGroups <-cut(car_count_by_VehicleAge$MMRCurrAucAvgPrice, breaks = c(quantile(car_count_by_VehicleAge$MMRCurrAucAvgPrice, probs = c(0,0.25,0.5,0.75,1))),
     labels = c(str_c(quantile(car_count_by_VehicleAge$MMRCurrAucAvgPrice,probs = 0),quantile(car_count_by_VehicleAge$MMRCurrAucAvgPrice,probs = 0.25),sep = " to "),str_c(quantile(car_count_by_VehicleAge$MMRCurrAucAvgPrice,probs = 0.25),quantile(car_count_by_VehicleAge$MMRCurrAucAvgPrice,probs = 0.5),sep = " to "),str_c(quantile(car_count_by_VehicleAge$MMRCurrAucAvgPrice,probs = 0.5),quantile(car_count_by_VehicleAge$MMRCurrAucAvgPrice,probs = 0.75),sep = " to "),str_c(quantile(car_count_by_VehicleAge$MMRCurrAucAvgPrice,probs = 0.75),quantile(car_count_by_VehicleAge$MMRCurrAucAvgPrice,probs = 1),sep = " to ")), right = FALSE, include.lowest=TRUE)
car_count_by_VehicleAge$MMRCurrAucAvgPriceGroups<-as.factor(car_count_by_VehicleAge$MMRCurrAucAvgPriceGroups)


current_auc_avg_price<-ggplot(car_count_by_VehicleAge, aes(IsBadBuy, group = MMRCurrAucAvgPriceGroups)) + 
  geom_bar(aes(y = ..prop.., fill = IsBadBuy), stat="count",fill = "#FF6666") +
  geom_text(aes(label = scales::percent(..prop..),
                y = ..prop..), stat = "count", vjust = -0.5) +
  labs(y = "Percent",fill = "IsBadBuy") + ggtitle("% of Bad Buy VS MMRCurrentAuctionAveragePrice groups")+
  facet_grid(~MMRCurrAucAvgPriceGroups) + 
  scale_y_continuous(labels = scales::percent)
current_auc_avg_price
```


#### 6. Proportion of Bad Buy decreases with increase in Current Auction Clean Price
```{r}
car_count_by_VehicleAge$MMRCurrAucCleanPriceGroups <-cut(car_count_by_VehicleAge$MMRCurrAucCleanPrice, breaks = c(quantile(car_count_by_VehicleAge$MMRCurrAucCleanPrice, probs = c(0,0.25,0.5,0.75,1))),
     labels = c(str_c(quantile(car_count_by_VehicleAge$MMRCurrAucCleanPrice,probs = 0),quantile(car_count_by_VehicleAge$MMRCurrAucCleanPrice,probs = 0.25),sep = " to "),str_c(quantile(car_count_by_VehicleAge$MMRCurrAucCleanPrice,probs = 0.25),quantile(car_count_by_VehicleAge$MMRCurrAucCleanPrice,probs = 0.5),sep = " to "),str_c(quantile(car_count_by_VehicleAge$MMRCurrAucCleanPrice,probs = 0.5),quantile(car_count_by_VehicleAge$MMRCurrAucCleanPrice,probs = 0.75),sep = " to "),str_c(quantile(car_count_by_VehicleAge$MMRCurrAucCleanPrice,probs = 0.75),quantile(car_count_by_VehicleAge$MMRCurrAucCleanPrice,probs = 1),sep = " to ")), right = FALSE, include.lowest=TRUE)
car_count_by_VehicleAge$MMRCurrAucCleanPriceGroups<-as.factor(car_count_by_VehicleAge$MMRCurrAucCleanPriceGroups)


current_auc_clean_price<-ggplot(car_count_by_VehicleAge, aes(IsBadBuy, group = MMRCurrAucCleanPriceGroups)) + 
  geom_bar(aes(y = ..prop.., fill = IsBadBuy), stat="count",fill = "#FF6666") +
  geom_text(aes(label = scales::percent(..prop..),
                y = ..prop..), stat = "count", vjust = -0.5) +
  labs(y = "Percent",fill = "IsBadBuy") + ggtitle("% of Bad Buy VS MMRCurrAucCleanPriceGroups groups")+
  facet_grid(~MMRCurrAucCleanPriceGroups) + 
  scale_y_continuous(labels = scales::percent)
current_auc_clean_price
```


#### 7.No concrete conclusion on Current Retail Avg Price
```{r}
car_count_by_VehicleAge$MMRCurrRetailAvgPriceGroups <-cut(car_count_by_VehicleAge$MMRCurrRetailAvgPrice, breaks = c(quantile(car_count_by_VehicleAge$MMRCurrRetailAvgPrice, probs = c(0,0.25,0.5,0.75,1))),
     labels = c(str_c(quantile(car_count_by_VehicleAge$MMRCurrRetailAvgPrice,probs = 0),quantile(car_count_by_VehicleAge$MMRCurrRetailAvgPrice,probs = 0.25),sep = " to "),str_c(quantile(car_count_by_VehicleAge$MMRCurrRetailAvgPrice,probs = 0.25),quantile(car_count_by_VehicleAge$MMRCurrRetailAvgPrice,probs = 0.5),sep = " to "),str_c(quantile(car_count_by_VehicleAge$MMRCurrRetailAvgPrice,probs = 0.5),quantile(car_count_by_VehicleAge$MMRCurrRetailAvgPrice,probs = 0.75),sep = " to "),str_c(quantile(car_count_by_VehicleAge$MMRCurrRetailAvgPrice,probs = 0.75),quantile(car_count_by_VehicleAge$MMRCurrRetailAvgPrice,probs = 1),sep = " to ")), right = FALSE, include.lowest=TRUE)
car_count_by_VehicleAge$MMRCurrRetailAvgPriceGroups<-as.factor(car_count_by_VehicleAge$MMRCurrRetailAvgPriceGroups)


ggplot(car_count_by_VehicleAge, aes(IsBadBuy, group = MMRCurrRetailAvgPriceGroups)) + 
  geom_bar(aes(y = ..prop.., fill = IsBadBuy), stat="count") +
  geom_text(aes(label = scales::percent(..prop..),
                y = ..prop..), stat = "count", vjust = -0.5) +
  labs(y = "Percent",fill = "IsBadBuy") + ggtitle("% of Bad Buy VS MMRCurrRetailAvgPriceGroups groups")+
  facet_grid(~MMRCurrRetailAvgPriceGroups) + 
  scale_y_continuous(labels = scales::percent)

```

#### 8.No concrete conclusion on Current Retail Clean Price
```{r}
car_count_by_VehicleAge$MMRCurrRetailCleanPriceGroups <-cut(car_count_by_VehicleAge$MMRCurrRetailAvgPrice, breaks = c(quantile(car_count_by_VehicleAge$MMRCurrRetailCleanPrice, probs = c(0,0.25,0.5,0.75,1))),
     labels = c(str_c(quantile(car_count_by_VehicleAge$MMRCurrRetailCleanPrice,probs = 0),quantile(car_count_by_VehicleAge$MMRCurrRetailCleanPrice,probs = 0.25),sep = " to "),str_c(quantile(car_count_by_VehicleAge$MMRCurrRetailCleanPrice,probs = 0.25),quantile(car_count_by_VehicleAge$MMRCurrRetailCleanPrice,probs = 0.5),sep = " to "),str_c(quantile(car_count_by_VehicleAge$MMRCurrRetailCleanPrice,probs = 0.5),quantile(car_count_by_VehicleAge$MMRCurrRetailCleanPrice,probs = 0.75),sep = " to "),str_c(quantile(car_count_by_VehicleAge$MMRCurrRetailCleanPrice,probs = 0.75),quantile(car_count_by_VehicleAge$MMRCurrRetailCleanPrice,probs = 1),sep = " to ")), right = FALSE, include.lowest=TRUE)
car_count_by_VehicleAge$MMRCurrRetailCleanPriceGroups<-as.factor(car_count_by_VehicleAge$MMRCurrRetailCleanPriceGroups)


ggplot(car_count_by_VehicleAge, aes(IsBadBuy, group = MMRCurrRetailCleanPriceGroups)) + 
  geom_bar(aes(y = ..prop.., fill = IsBadBuy), stat="count") +
  geom_text(aes(label = scales::percent(..prop..),
                y = ..prop..), stat = "count", vjust = -0.5) +
  labs(y = "Percent",fill = "IsBadBuy") + ggtitle("% of Bad Buy VS MMRCurrRetailCleanPriceGroups groups")+
  facet_grid(~MMRCurrRetailCleanPriceGroups) + 
  scale_y_continuous(labels = scales::percent)

```


```{r}
#Create data
set.seed(1)
Ixos=car_buy_clean_df$VehBCost[which(car_buy_clean_df$IsBadBuy == 0)]    
Primadur=car_buy_clean_df$VehBCost[which(car_buy_clean_df$IsBadBuy == 1)] 

#First distribution
hist(Ixos, breaks=30, col=rgb(1,0,0,0.5), xlab="Vehicle Cost", 
     ylab="nbr of vehicles", main="distribution of Vehicle Cost" )

#Second with add=T to plot on top
hist(Primadur, breaks=30, col=rgb(0,0,1,0.5), add=T)

#Add legend
legend("topright", legend=c("Not_Bad_buy","Bad_buy"), col=c(rgb(1,0,0,0.5), 
     rgb(0,0,1,0.5)), pt.cex=2, pch=15 )
```

#### Correlation Matrix

```{r}
library(corrplot)

num_df <- car_buy_clean_df[,sapply(car_buy_clean_df, is.numeric)]
corMatrix <- cor(num_df)
#View(descrCor)
#print(descrCor)
corrplot(corMatrix)


corrplot(cor(num_df), method = "color", type = "upper")

```



```{r}
#newtest_df <- car_data[which(car_data$VehOdo > 100000),]

#Create data
set.seed(1)
Ixos=car_data$MMRCurrentRetailCleanPrice[which(car_data$IsBadBuy == 0)]    
Primadur=car_data$MMRCurrentRetailCleanPrice[which(car_data$IsBadBuy == 1)] 

#First distribution
hist(Ixos, breaks=30, col=rgb(1,0,0,0.5), xlab="height", 
     ylab="nbr of plants", main="distribution of height of 2 durum wheat varieties" )

#Second with add=T to plot on top
hist(Primadur, breaks=30, col=rgb(0,0,1,0.5), add=T)

#Add legend
legend("topright", legend=c("Ixos","Primadur"), col=c(rgb(1,0,0,0.5), 
     rgb(0,0,1,0.5)), pt.cex=2, pch=15 )
```



